Extracting all spectra for NEON mapped stems

### 2021-02-23 R/spectral-lib.Rmd
reinstalling / updating all packages, R, Rstudio, adding comments and working on spectral lib creation for consistency

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#install.packages('remotes')
#remotes::install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
library(sp)
#remotes::install_github('earthlab/neonhs')
library(neonhs)
library(dplyr)
library(here)
```

@@

zipsByProduct(dpID = "DP1.10098.001",
              savepath = out_dir,
              check.size = FALSE)
stackByTable(file.path(out_dir, "filesToStack10098"), folder = TRUE)
```

>>>>

```{r load-libraries, message=FALSE}
library(tidyverse)
library(neonUtilities)
#install.packages('remotes')
#remotes::install_github('NEONScience/NEON-geolocation/geoNEON', dependencies=TRUE)
library(geoNEON)
#install.packages('devtools')
#devtools::install_github('earthlab/neonhs')
library(neonhs)
library(dplyr)
library(here)
```

@@

# Download NEON observational data, Woody plant vegetation structure
neonUtilities::zipsByProduct(dpID = "DP1.10098.001",
              savepath = out_dir,
              check.size = FALSE)
stackByTable(file.path(out_dir, "filesToStack10098"), folder = TRUE)
```
